\chapter{Introduction}\label{secIntroduction}
Trading off risks against returns appears to be essential and vital for making a financial decision. Hence the econometric analysis of risk (volatility) becomes an important part in forecasting market tendency and supporting making financial decisions, such as portfolio diversification, risk management and derivative pricing. In the last 20 years volatility was a research hotspot in financial industry. Volatility is regarded as a parameter for evaluating the risk of assets return. Generally, the stronger the volatility is, the higher the risk is.

In the traditional financial models, the variance of the time series is always assumed as constant. However, it is found that the volatilities of financial time series have always the features of “clustering” and “fat tails”  \citep{Mandelbrot1963,EugeneF.Fama1965}. These features obviously are not consistent with the assumption of constant, so the traditional econometrical methods cannot analyze the time series variables efficiently in practice. To overcome this problem, several economists have carried out studies on researching and developing frameworks for evaluating volatility. Since Engle introduced the autoregressive conditional heteroskedasticity (ARCH) model \citep{Engle1982}, he extensions of ARCH model appeared and spread rapidly. Among the carried out researches, the Generalized ARCH (GARCH) model and its derivatives are most widely used \citep{Bollerslev1986}.

Instead of parametric models or nonparametric models, recently proposed semi parametric models will be introduced in details in this paper. According to many studies \citep{Gourieroux1992,Eubank1993}, preselected parametric models might be too restricted or too low-dimensional, which may not fit unexpected features and cause the misspecification. However, in nonparametric models, the parameters of the model cannot be estimated, and the model cannot be explained due to lack of specific functions. The semi parametric models do not need a prespecified function and is less sensitive to model misspecification. At the same time, the model can be also explained \citep{Di2011}.

In this paper, the definition, estimation, some properties of semi-parametric models and the methods of bandwidth selection are discussed. Furthermore, according to the study of the semi-parametric GARCH model and semi-parametric asymmetric power ARCH model, which are introduced by Feng \citep{Feng2004} \citep{FengYuanhua;Sun2013}, the semi-parametric method will trying to enter into exponential GARCH and component GARCH models. Then, the discussed semi-parametric models, i.e. semi-parametric APARCH, EGARCH and CGARCH models, are applied to the stock prices of BMW and Allianz from January 2006 to September 2014. Different from other papers, to get the more exact analyzing results the fixed trading time points will be used in this paper. (Lack of a simple conclusion of the analysis)

The plan of this paper is as follows. In section 2 the parametric models are introduced. The semi-parametric models are described in section 3. Section 4 reports the application of the semi-parametric models to the stock prices of BMW and Allianz and the empirical results on the volatility of the selected prices. Finally, this paper is concluded in section 5.